---
title: "Fig3"
author: "Atsuki Taniguchi"
date: "`r format(Sys.time(), '%Y年%m月%d日')`"
output:
 html_document:
  toc: true
  toc_float: true
  toc_depth: 6 
  number_sections: true
---
```{=html}
<style>
div.blue pre { background-color:lightblue !important; }
div.blue pre.r { background-color:lightyellow !important; }
</style>
```
<div class = "blue">

```{r setup, include=FALSE}
library(kableExtra)

knitr::opts_chunk$set(cache=FALSE, echo=FALSE, comment="", warning=FALSE, message=FALSE, fig.width=10, fig.height=8)

```

```{r}
# Helper function for package info
getPkgInfo <- function(info){
  #info <- sessionInfo()
  pkg <- info$otherPkgs
  pkg.info <- t(sapply(pkg, function(p){
    out <- matrix(c(Package=ifelse(is.null(p$Package),"-",p$Package),
                    Version=ifelse(is.null(p$Version),"-",p$Version),
                    Title=ifelse(is.null(p$Title),"-",p$Title),
                    License=ifelse(is.null(p$License),"-",p$License),
                    Repository=ifelse(is.null(p$Repository),"-",p$Repository)), nrow=1, ncol=5)
  }))
  colnames(pkg.info) <- c("Package","Version","Overview","License","Repository")
  return(pkg.info)
}
```

# Loading packages
```{r}
library(Seurat);library(tidyverse);library(CellChat);library(nichenetr) ;library(pheatmap);library(patchwork);library(ggrepel);library(future) 
```

# EREG Expression Analysis: Fig3A,3B,3C,S3B
```{r}
set.seed(123)

obj <- readRDS("~/Primarytumor/tumor_integrated_LR.RDS")
Idents(obj) <- "RAS"

obj_R <-subset(obj, Sidedness=="R")
obj_L <-subset(obj, Sidedness=="L")

FeaturePlot(obj_R, features = "EREG", split.by = "RAS") #Fig3A-1
FeaturePlot(obj_L, features = "EREG", split.by = "RAS") #Fig3A-2

obj@meta.data$Side_RAS <- NA

obj@meta.data$Side_RAS[obj@meta.data$RAS == "wt" & obj@meta.data$Sidedness == "L"] <- "Left_RAS-wild"
obj@meta.data$Side_RAS[obj@meta.data$RAS == "mut" & obj@meta.data$Sidedness == "L"] <- "Left_RAS-mut"
obj@meta.data$Side_RAS[obj@meta.data$RAS == "wt" & obj@meta.data$Sidedness == "R"] <- "Right_RAS-wild"
obj@meta.data$Side_RAS[obj@meta.data$RAS == "mut" & obj@meta.data$Sidedness == "R"] <- "Right_RAS-mut"

DotPlot(obj, features = "EREG", scale = FALSE, group.by = "Side_RAS") #Fig3B
DotPlot(obj, features = c("AREG","EGF", "TGFA", "BTC", "EPGN", "HBEGF"), scale = FALSE, group.by = "Side_RAS") #Fig3C
DotPlot(obj, features = "EREG", scale = FALSE, group.by = "seurat_clusters") #SFig3B
```

#Cell Type Proportions by Condition/Efficacy: Fig3D
```{r}
sc <- readRDS("~/Primarytumor/merge_rpca_EGFR.RDS")

sc@meta.data$cell_type[Idents(sc) == 11] <- "Pericyte"

sc_F <- subset(sc, cell_type=="Fibroblast")
sc_CAF <- subset(sc_F, condition=="Tumor")
CAF <- colnames(sc_CAF) 
sc$cell_type[CAF] <- "CAF"

sc_Fibro <- subset(sc_F, condition=="Normal")
Fibro <- colnames(sc_Fibro) 
sc$cell_type[Fibro] <- "NF"

sc_meta_data <- as.data.frame(sc@meta.data)

data_processed <- sc_meta_data %>%
  filter(cell_type != "Epithelial cell",
         cell_type != "not.defined", 
         !is.na(cell_type)) %>%  
  mutate(Group = case_when(
    condition == "Normal" ~ "Normal",
    condition == "Tumor" & EGFR_efficacy == "EGFR_eligible" ~ "EGFR_eligible",
    condition == "Tumor" & EGFR_efficacy == "EGFR_ineligible" ~ "EGFR_ineligible"
  )) %>%
  filter(!is.na(Group)) %>%
  dplyr::select(Group, cell_type)

data_processed$cell_type <- factor(data_processed$cell_type, levels = c("NF","CAF","Pericyte", "Myeloid cell","T cell", "B cell","Plasma cell","Endothelial cell"))

data_summary <- data_processed %>%
  dplyr::count(Group, cell_type) %>%
  group_by(Group) %>%
  mutate(Freq = n / sum(n))

custom_dark_colors <- c(
  "NF"               = "#3366CC",  
  "CAF"              = "#DC3912",   
  "Pericyte"         = "#E67300",  
  "Myeloid cell"      = "#990099",   
  "T cell"           = "#66AA00",  
  "B cell"           = "#B82E2E",  
  "Plasma cell"      = "#316395", 
  "Endothelial cell" = "#AAAA11"   
)

ggplot(data_summary, aes(x = Group, y = Freq, fill = cell_type)) +
  geom_bar(stat="identity", position="stack") +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_manual(values = custom_dark_colors) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_blank(),
        text = element_text(family = "Arial", size = 10),
    axis.text = element_text(size = 10)) #Fig3D
```

# CellChat Analysis: EGFR_ineligible vs EGFR_eligible
##Create CellChat object for EGFR_ineligible group
```{r}
set.seed(123)

sc <- readRDS("~/Primarytumor/merge_rpca_EGFR.RDS")
sc <- subset(sc, condition=="Tumor")
sc@meta.data$cell_type[Idents(sc) == 11] <- "Pericyte"

sc@meta.data <- sc@meta.data %>%
  mutate(cell_type = ifelse(cell_type == "Epithelial cell", "Cancer cell", cell_type))

sc <- subset(sc, cell_type %in% c(
    "B cell", "Endothelial cell", "Cancer cell", 
    "Fibroblast", "Myeloid cell", "Plasma cell", "T cell"))

sc_ineligible <- subset(sc, EGFR_efficacy=="EGFR_ineligible")

data.input <- sc_ineligible[["RNA"]]$data
meta <-  sc_ineligible@meta.data %>% dplyr::select(cell_type)
colnames(meta) <- "labels"

cellChat_ineligible <- createCellChat(object = data.input, meta  = meta, group.by = "labels")

future::plan("multicore", workers = 12)
options(future.globals.maxSize = 10000 * 1024^2)

# Ligand-receptor interactions in CellChat database for human
CellChatDB <- CellChatDB.human

# Subset CellChatDB databse by only including interactions of interest
CellChatDB.use <- subsetDB(CellChatDB)

# set DB
cellChat_ineligible@DB <- CellChatDB.use

# Subset the expression data of signaling genes for saving computation cost
# update object@data.signaling
cellChat_ineligible <- subsetData(cellChat_ineligible)

# Identify over-expressed signaling genes associated with each cell group
# return object@var.features

cellChat_ineligible <- identifyOverExpressedGenes(cellChat_ineligible)

# Identify over-expressed ligand-receptor interactions (pairs) within the used CellChatDB
# return object@LR$LRsig
cellChat_ineligible <- identifyOverExpressedInteractions(cellChat_ineligible)

# To further speed up on large-scale datasets, USER can downsample the data using the function 'subset' from Seurat package (e.g., pbmc.small <- subset(pbmc, downsample = 500)), or using the function 'sketchData' from CellChat, in particular for the large cell clusters;
# return object@net$prob
cellChat_ineligible <- computeCommunProb(cellChat_ineligible, type = "triMean")

# Filter cell-cell communication if there are only few number of cells in certain cell groups
# update object@net
cellChat_ineligible <- filterCommunication(cellChat_ineligible, min.cells = 10)

# Compute the communication probability on signaling pathway level by summarizing all related ligands/receptors
# return object@netP
cellChat_ineligible <- computeCommunProbPathway(cellChat_ineligible)

# Calculate the aggregated network by counting the number of links or summarizing the communication probability
# return object@net$count, object@net$weight, object@net$sum
cellChat_ineligible <- aggregateNet(cellChat_ineligible)

saveRDS(cellChat_ineligible,"~/Primarytumor/cellchat_EGFR_ineligible.rds")
```

##Create CellChat object for EGFR_eligible group
```{r}
set.seed(123)

sc_eligible <- subset(sc, EGFR_efficacy=="EGFR_eligible")

data.input <- sc_eligible[["RNA"]]$data
meta <-  sc_eligible@meta.data %>% dplyr::select(cell_type)
colnames(meta) <- "labels"

cellChat_eligible <- createCellChat(object = data.input, meta  = meta, group.by = "labels")

future::plan("multicore", workers = 12)
options(future.globals.maxSize = 10000 * 1024^2)

# Ligand-receptor interactions in CellChat database for human
CellChatDB <- CellChatDB.human

# Subset CellChatDB databse by only including interactions of interest
CellChatDB.use <- subsetDB(CellChatDB)

# set DB
cellChat_eligible@DB <- CellChatDB.use

# Subset the expression data of signaling genes for saving computation cost
# update object@data.signaling
cellChat_eligible <- subsetData(cellChat_eligible)

# Identify over-expressed signaling genes associated with each cell group
# return object@var.features

cellChat_eligible <- identifyOverExpressedGenes(cellChat_eligible)

# Identify over-expressed ligand-receptor interactions (pairs) within the used CellChatDB
# return object@LR$LRsig
cellChat_eligible <- identifyOverExpressedInteractions(cellChat_eligible)

# To further speed up on large-scale datasets, USER can downsample the data using the function 'subset' from Seurat package (e.g., pbmc.small <- subset(pbmc, downsample = 500)), or using the function 'sketchData' from CellChat, in particular for the large cell clusters;
# return object@net$prob
cellChat_eligible <- computeCommunProb(cellChat_eligible, type = "triMean")

# Filter cell-cell communication if there are only few number of cells in certain cell groups
# update object@net
cellChat_eligible <- filterCommunication(cellChat_eligible, min.cells = 10)

# Compute the communication probability on signaling pathway level by summarizing all related ligands/receptors
# return object@netP
cellChat_eligible <- computeCommunProbPathway(cellChat_eligible)

# Calculate the aggregated network by counting the number of links or summarizing the communication probability
# return object@net$count, object@net$weight, object@net$sum
cellChat_eligible <- aggregateNet(cellChat_eligible)

saveRDS(cellChat_eligible,"~/Primarytumor/cellchat_EGFR_eligible.rds")
```

##Compare cell-cell communication between ineligible and eligible groups
```{r}
cellchat_eligible <- readRDS("~/Primarytumor/cellchat_EGFR_eligible.rds")
cellchat_eligible <- netAnalysis_computeCentrality(cellchat_eligible, slot.name = "netP")

cellchat_ineligible <- readRDS("~/Primarytumor/cellchat_EGFR_ineligible.rds")
cellchat_ineligible <- netAnalysis_computeCentrality(cellchat_ineligible, slot.name = "netP")

object.list <- list(
  EGFR_ineligible = cellchat_ineligible,
  EGFR_eligible = cellchat_eligible
  )

cellchat <- mergeCellChat(object.list, cell.prefix = TRUE, add.names = names(object.list))
cellchat
```

## Differential interaction heatmap (Comparison): Fig3E
```{r}
netVisual_heatmap(cellchat)
netVisual_heatmap(cellchat, measure = "weight") #Fig3E
```

## Circle plots for EGF and CSF pathways: Fig3F-1～4
```{r}
# Circle plot
pathways.show <- c("EGF") 
weight.max <- getMaxWeight(object.list, slot.name = c("netP"), attribute = pathways.show) # control the edge weights across different datasets
par(mfrow = c(1,2), xpd=TRUE)
for (i in 1:length(object.list)) {
  tiff(paste0("~/Primarytumor/paper/Figure3/Fig3F-",i, ".tiff"), 
       width = 10, height = 10, units = "cm", res = 600, compression = "lzw")
  netVisual_aggregate(object.list[[i]], signaling = pathways.show, layout = "circle", 
                      edge.weight.max = weight.max[1], edge.width.max = 8, 
                      signaling.name = names(object.list)[i], arrow.size=0.5)
  dev.off()
} #Fig3F-1,2

# Circle plot
pathways.show <- c("CSF") 
weight.max <- getMaxWeight(object.list, slot.name = c("netP"), attribute = pathways.show) # control the edge weights across different datasets
for (i in 1:length(object.list)) {
  tiff(paste0("~/Primarytumor/paper/Figure3/Fig3F-", i+2, ".tiff"), 
       width = 10, height = 10, units = "cm", res = 600, compression = "lzw")
  netVisual_aggregate(object.list[[i]], signaling = pathways.show, layout = "circle", 
                      edge.weight.max = weight.max[1], edge.width.max = 10, 
                      signaling.name = names(object.list)[i], arrow.size=0)
  dev.off()
} #Fig3F-3,4
```

## Rank signaling pathways comparing Eligible vs Ineligible: suppleFig3C,D
```{r}
netP_eligible <- cellchat_eligible@netP$prob
netP_ineligible <- cellchat_ineligible@netP$prob

cellchat <- mergeCellChat(object.list, cell.prefix = TRUE, add.names = names(object.list))

cellchat@netP$prob <- list(
  EGFR_eligible = netP_eligible,
  EGFR_ineligible = netP_ineligible
)

# rankNet
#SFig3C: Rank pathways (Cancer -> Fibroblast)
rankNet(cellchat, mode = "comparison", stacked = TRUE, sources.use = "Cancer cell", targets.use = "Fibroblast")+
  theme(
    legend.position = "bottom"
  ) #SFig3C

#SFig3D: Rank pathways (Fibroblast -> Myeloid cell)
rankNet(cellchat, mode = "comparison", stacked = TRUE, sources.use = "Fibroblast", targets.use = "Myeloid cell")+
  theme(
    legend.position = "bottom"
  ) #SFig3D
```

# NicheNet Analysis (Epithelial -> Fibroblast): Fig3G
```{r}
seuratObj <- readRDS("~/Primarytumor/merge_rpca_EGFR.RDS")
seuratObj <- subset(seuratObj, condition=="Tumor")
seuratObj@meta.data$cell_type[Idents(seuratObj) == 11] <- "Pericyte"

seuratObj <- subset(seuratObj, cell_type %in% c("Epithelial cell", "Fibroblast"))

Idents(seuratObj) <- "cell_type"

options(timeout = 600)

organism <- "human"

if(organism == "human"){
  lr_network <- readRDS(url("https://zenodo.org/record/7074291/files/lr_network_human_21122021.rds"))
  ligand_target_matrix <- readRDS(url("https://zenodo.org/record/7074291/files/ligand_target_matrix_nsga2r_final.rds"))
  weighted_networks <- readRDS(url("https://zenodo.org/record/7074291/files/weighted_networks_nsga2r_final.rds"))
} else if(organism == "mouse"){
  lr_network <- readRDS(url("https://zenodo.org/record/7074291/files/lr_network_mouse_21122021.rds"))
  ligand_target_matrix <- readRDS(url("https://zenodo.org/record/7074291/files/ligand_target_matrix_nsga2r_final_mouse.rds"))
  weighted_networks <- readRDS(url("https://zenodo.org/record/7074291/files/weighted_networks_nsga2r_final_mouse.rds"))
}

receiver = "Fibroblast"
expressed_genes_receiver <- get_expressed_genes(receiver, seuratObj, pct = 0.05)

all_receptors <- unique(lr_network$to)  
expressed_receptors <- intersect(all_receptors, expressed_genes_receiver)

potential_ligands <- lr_network %>% filter(to %in% expressed_receptors) %>% pull(from) %>% unique()

sender_celltypes <- "Epithelial cell"

expressed_genes_sender <- get_expressed_genes(sender_celltypes, seuratObj, 0.40)

potential_ligands_focused <- intersect(potential_ligands, expressed_genes_sender)

potential_ligands_focused
# [1] "ADAM10"   "ADAM15"   "ADAM9"    "ADGRE5"   "ADM"     
# [6] "ANG"      "ANXA2"    "APP"      "AREG"     "ARF1"    
#[11] "ATP1B1"   "AZGP1"    "B2M"      "BACE2"    "BMP4"    
#[16] "CALM1"    "CALM2"    "CALM3"    "CALR"     "CD320"   
#[21] "CD44"     "CD47"     "CD55"     "CD9"      "CD99"    
#[26] "CDCP1"    "CDH1"     "CEACAM1"  "CEACAM6"  "CKLF"    
#[31] "CLDN1"    "CMTM8"    "COPA"     "CRB3"     "CTSD"    
#[36] "CXCL16"   "CXCL2"    "CXCL3"    "DSC2"     "EDN1"    
#[41] "EFNA1"    "EFNB1"    "EFNB2"    "EREG"     "EZR"     
#[46] "F11R"     "FAM3C"    "GAS6"     "GDF15"    "GLG1"    
#[51] "GNAS"     "GPI"      "GRN"      "GSTP1"    "HBEGF"   
#[56] "HLA-A"    "HLA-B"    "HLA-E"    "HMGB1"    "IFITM1"  
#[61] "IGFBP4"   "IL18"     "ITGB1"    "ITM2B"    "LAMB3"   
#[66] "LAMC2"    "LCN2"     "LEFTY1"   "LGALS3"   "LGALS3BP"
#[71] "LGALS9"   "LIPH"     "LRPAP1"   "MDK"      "MIF"     
#[76] "NAMPT"    "NECTIN2"  "NUCB2"    "OCLN"     "PRSS3"   
#[81] "PSAP"     "PTDSS1"   "PTPRK"    "RTN4"     "S100A4"  
#[86] "SARAF"    "SDC4"     "SERPINA1" "SLPI"     "SPINK1"  
#[91] "ST14"     "TGFBI"    "TGOLN2"   "TIMP1"    "TNFRSF14"
#[96] "TNFSF10"  "TSPAN3"   "VEGFA"    "ZG16B"  

length(expressed_genes_sender)
## [1] 3509
length(potential_ligands)
## [1] 904
length(potential_ligands_focused)
## [1] 99

condition_oi <-  "EGFR_eligible"
condition_reference <- "EGFR_ineligible"

seurat_obj_receiver <- subset(seuratObj, idents = receiver)

DE_table_receiver <-  FindMarkers(object = seurat_obj_receiver,
                                  ident.1 = condition_oi, ident.2 = condition_reference,
                                  group.by = "EGFR_efficacy",
                                  min.pct = 0.05) %>% rownames_to_column("gene")

geneset_oi <- DE_table_receiver %>% filter(p_val_adj <= 0.1 & abs(avg_log2FC) >= 0.4) %>% pull(gene)
geneset_oi <- geneset_oi %>% .[. %in% rownames(ligand_target_matrix)]

# Define background_expressed_genes
background_expressed_genes <- expressed_genes_receiver %>% .[. %in% rownames(ligand_target_matrix)]

length(background_expressed_genes)
## [1] 10143
length(geneset_oi)
## [1] 1373

# Run NicheNet ligand activity prediction
ligand_activities <- predict_ligand_activities(geneset = geneset_oi,
                                               background_expressed_genes = background_expressed_genes,
                                               ligand_target_matrix = ligand_target_matrix,
                                               potential_ligands = potential_ligands)

ligand_activities <- ligand_activities %>% 
  arrange(-aupr_corrected) %>% 
  mutate(rank = rank(dplyr::desc(aupr_corrected)))

ligand_activities
# A tibble: 99 × 6
#   test_ligand auroc  aupr aupr_corrected pearson  rank
#   <chr>       <dbl> <dbl>          <dbl>   <dbl> <dbl>
# 1 ADM         0.598 0.219         0.0849  0.120      4
# 2 ANG         0.604 0.208         0.0745  0.120      6
# 3 BMP4        0.586 0.202         0.0683  0.107     19
# 4 OCLN        0.595 0.199         0.0652  0.122     27
# 5 S100A4      0.591 0.199         0.0651  0.117     28
# 6 ADAM9       0.582 0.199         0.0645  0.105     31
# 7 TIMP1       0.586 0.197         0.0632  0.0955    42
# 8 ITM2B       0.585 0.197         0.0631  0.0959    44
# 9 EFNA1       0.588 0.197         0.0631  0.111     45
#10 CDCP1       0.579 0.196         0.0621  0.108     53
# ℹ 89 more rows
# ℹ Use `print(n = ...)` to see more rows

p_hist_lig_activity <- ggplot(ligand_activities, aes(x=aupr_corrected)) + 
  geom_histogram(color="black", fill="darkorange")  + 
  geom_vline(aes(xintercept=min(ligand_activities %>% top_n(30, aupr_corrected) %>% pull(aupr_corrected))),
             color="red", linetype="dashed", size=1) + 
  labs(x="ligand activity (PCC)", y = "# ligands") +
  theme_classic()

p_hist_lig_activity

# Select top 30 ligands based on AUPR
best_upstream_ligands <- ligand_activities %>% top_n(30, aupr_corrected) %>% arrange(-aupr_corrected) %>% pull(test_ligand)

vis_ligand_aupr <- ligand_activities %>% filter(test_ligand %in% best_upstream_ligands) %>%
  column_to_rownames("test_ligand") %>% dplyr::select(aupr_corrected) %>% arrange(aupr_corrected) %>% as.matrix(ncol = 1)

(make_heatmap_ggplot(vis_ligand_aupr,
                     "Prioritized ligands", "Ligand activity", 
                     legend_title = "AUPR", color = "darkorange") + 
    theme(axis.text.x.top = element_blank())) 

# Analysis focusing on sender cell
ligand_activities_all <- ligand_activities 
best_upstream_ligands_all <- best_upstream_ligands

ligand_activities <- ligand_activities %>% filter(test_ligand %in% potential_ligands_focused)
best_upstream_ligands <- ligand_activities %>% top_n(30, aupr_corrected) %>% arrange(-aupr_corrected) %>%
  pull(test_ligand) %>% unique()

ligand_aupr_matrix <- ligand_activities %>% filter(test_ligand %in% best_upstream_ligands) %>%
  column_to_rownames("test_ligand") %>% dplyr::select(aupr_corrected) %>% arrange(aupr_corrected)
vis_ligand_aupr <- as.matrix(ligand_aupr_matrix, ncol = 1) 

p_ligand_aupr <- make_heatmap_ggplot(vis_ligand_aupr,
                     "Top 30 Prioritized ligands genes", "Ligand activity", 
                     legend_title = "AUPR", color = "darkorange") + 
    theme(axis.text.x.top = element_blank())

p_ligand_aupr <- p_ligand_aupr + 
  theme(legend.key.height = unit(0.3, "cm"),
        legend.key.width = unit(1.0, "cm"))

p_ligand_aupr #Fig3G-1

# Receptor plot
ligand_receptor_links_df <- get_weighted_ligand_receptor_links(
  best_upstream_ligands, expressed_receptors,
  lr_network, weighted_networks$lr_sig) 

vis_ligand_receptor_network <- prepare_ligand_receptor_visualization(
  ligand_receptor_links_df,
  best_upstream_ligands,
  order_hclust = "both") 

p_ligand_receptor <- make_heatmap_ggplot(t(vis_ligand_receptor_network), 
                     y_name = "Ligands", x_name = "Receptors",  
                     color = "mediumvioletred", legend_title = "Prior interaction potential")

p_ligand_receptor

# Target gene plot
active_ligand_target_links_df <- best_upstream_ligands %>%
  lapply(get_weighted_ligand_target_links,
         geneset = geneset_oi,
         ligand_target_matrix = ligand_target_matrix,
         n = 100) %>%
  bind_rows() %>% drop_na()

active_ligand_target_links <- prepare_ligand_target_visualization(
  ligand_target_df = active_ligand_target_links_df,
  ligand_target_matrix = ligand_target_matrix,
  cutoff = 0) 

order_ligands <- intersect(best_upstream_ligands, colnames(active_ligand_target_links)) %>% rev()
order_targets <- active_ligand_target_links_df$target %>% unique() %>% intersect(rownames(active_ligand_target_links))

vis_ligand_target <- t(active_ligand_target_links[order_targets,order_ligands])

p_ligand_target <- make_heatmap_ggplot(vis_ligand_target, "Prioritized ligands", "Predicted target genes",
                    color = "purple", legend_title = "Regulatory potential") +
  scale_fill_gradient2(low = "whitesmoke",  high = "purple")

p_ligand_target

# Target gene of EREG
ereg_targets <- active_ligand_target_links_df %>%
  filter(ligand == "EREG") %>%
  pull(target) %>%
  unique()

vis_ereg_target <- active_ligand_target_links[ereg_targets, "EREG", drop = FALSE] 

tiff("~/Primarytumor/paper/Fig3/Fig3G-2.tiff", 
     width = 4, height = 8, units = "cm", res = 600, compression = "lzw")
pheatmap(
  vis_ereg_target,
  scale = "none",
  cluster_rows = FALSE,
  cluster_cols = FALSE,
  clustering_method = "ward.D2",
  border_color = NA,
  cellwidth = 10,
  cellheight = 10,
  fontsize = 6,
  legend = FALSE,
  color = colorRampPalette(c("whitesmoke", "purple"))(100)
)
dev.off() #Fig3G-2
```

# Session Information
```{r echo=FALSE}
sessionInfo()
#R version 4.4.0 (2024-04-24 ucrt)
#Platform: x86_64-w64-mingw32/x64
#Running under: Windows 11 x64 (build 26100)

#Matrix products: default


#locale:
#[1] LC_COLLATE=Japanese_Japan.utf8  LC_CTYPE=Japanese_Japan.utf8   
#[3] LC_MONETARY=Japanese_Japan.utf8 LC_NUMERIC=C                   
#[5] LC_TIME=Japanese_Japan.utf8    

#time zone: Asia/Tokyo
#tzcode source: internal

#attached base packages:
#[1] stats     graphics  grDevices utils     datasets  methods   base     

#other attached packages:
# [1] future_1.34.0       ggrepel_0.9.6       patchwork_1.3.0    
# [4] pheatmap_1.0.12     nichenetr_2.1.7     CellChat_2.1.2     
# [7] Biobase_2.64.0      BiocGenerics_0.52.0 igraph_2.1.4       
#[10] lubridate_1.9.4     forcats_1.0.0       stringr_1.5.1      
#[13] dplyr_1.1.4         purrr_1.0.4         readr_2.1.5        
#[16] tidyr_1.3.1         tibble_3.2.1        ggplot2_3.5.1      
#[19] tidyverse_2.0.0     Seurat_5.2.1        SeuratObject_5.0.2 
#[22] sp_2.2-0            kableExtra_1.4.0   

#loaded via a namespace (and not attached):
#  [1] IRanges_2.38.1              coin_1.4-3                 
#  [3] nnet_7.3-20                 goftest_1.2-3              
#  [5] TH.data_1.1-3               vctrs_0.6.5                
#  [7] spatstat.random_3.3-3       digest_0.6.37              
#  [9] png_0.1-8                   shape_1.4.6.1              
# [11] proxy_0.4-27                registry_0.5-1             
# [13] deldir_2.0-4                parallelly_1.43.0          
# [15] MASS_7.3-65                 reshape2_1.4.4             
# [17] httpuv_1.6.15               foreach_1.5.2              
# [19] withr_3.0.2                 xfun_0.52                  
# [21] ggpubr_0.6.0                survival_3.8-3             
# [23] systemfonts_1.2.2           zoo_1.8-13                 
# [25] GlobalOptions_0.1.2         gtools_3.9.5               
# [27] pbapply_1.7-2               argparse_2.2.5             
# [29] Formula_1.2-5               promises_1.3.2             
# [31] httr_1.4.7                  rstatix_0.7.2              
# [33] globals_0.16.3              fitdistrplus_1.2-2         
# [35] rstudioapi_0.17.1           UCSC.utils_1.2.0           
# [37] miniUI_0.1.1.1              generics_0.1.3             
# [39] base64enc_0.1-3             ggalluvial_0.12.5          
# [41] S4Vectors_0.42.1            zlibbioc_1.50.0            
# [43] randomForest_4.7-1.2        polyclip_1.10-7            
# [45] GenomeInfoDbData_1.2.13     SparseArray_1.6.1          
# [47] xtable_1.8-4                doParallel_1.0.17          
# [49] evaluate_1.0.3              S4Arrays_1.4.1             
# [51] hms_1.1.3                   GenomicRanges_1.56.1       
# [53] irlba_2.3.5.1               colorspace_2.1-1           
# [55] visNetwork_2.1.2            ggnetwork_0.5.13           
# [57] ROCR_1.0-11                 reticulate_1.42.0          
# [59] spatstat.data_3.1-6         magrittr_2.0.3             
# [61] lmtest_0.9-40               later_1.4.2                
# [63] modeltools_0.2-23           lattice_0.22-6             
# [65] spatstat.geom_3.3-6         NMF_0.28                   
# [67] future.apply_1.11.3         scattermore_1.2            
# [69] shadowtext_0.1.4            cowplot_1.1.3              
# [71] matrixStats_1.5.0           RcppAnnoy_0.0.22           
# [73] Hmisc_5.2-3                 class_7.3-23               
# [75] pillar_1.10.2               nlme_3.1-168               
# [77] iterators_1.0.14            sna_2.8                    
# [79] gridBase_0.4-7              caTools_1.18.3             
# [81] compiler_4.4.0              RSpectra_0.16-2            
# [83] stringi_1.8.7               gower_1.0.2                
# [85] tensor_1.5                  SummarizedExperiment_1.36.0
# [87] plyr_1.8.9                  crayon_1.5.3               
# [89] abind_1.4-8                 locfit_1.5-9.12            
# [91] rjags_4-17                  sandwich_3.1-1             
# [93] libcoin_1.0-10              fastcluster_1.2.6          
# [95] codetools_0.2-20            multcomp_1.4-28            
# [97] recipes_1.2.1               bslib_0.9.0                
# [99] e1071_1.7-16                GetoptLong_1.0.5           
#[101] plotly_4.10.4               mime_0.13                  
#[103] splines_4.4.0               circlize_0.4.16            
#[105] Rcpp_1.0.14                 fastDummies_1.7.5          
#[107] knitr_1.50                  clue_0.3-66                
#[109] checkmate_2.3.2             listenv_0.9.1              
#[111] infercnv_1.22.0             ggsignif_0.6.4             
#[113] Matrix_1.7-2                statmod_1.5.0              
#[115] tzdb_0.5.0                  svglite_2.1.3              
#[117] phyclust_0.1-34             tweenr_2.0.3               
#[119] pkgconfig_2.0.3             network_1.19.0             
#[121] tools_4.4.0                 cachem_1.1.0               
#[123] viridisLite_0.4.2           fastmap_1.2.0              
#[125] rmarkdown_2.29              scales_1.3.0               
#[127] grid_4.4.0                  ica_1.0-3                  
#[129] broom_1.0.8                 sass_0.4.9                 
#[131] coda_0.19-4.1               FNN_1.1.4.1                
#[133] BiocManager_1.30.25         dotCall64_1.2              
#[135] carData_3.0-5               RANN_2.6.2                 
#[137] rpart_4.1.24                farver_2.1.2               
#[139] yaml_2.3.10                 foreign_0.8-90             
#[141] MatrixGenerics_1.18.1       DiagrammeR_1.0.11          
#[143] cli_3.6.3                   stats4_4.4.0               
#[145] lifecycle_1.0.4             caret_7.0-1                
#[147] uwot_0.2.3                  mvtnorm_1.3-3              
#[149] lambda.r_1.2.4              lava_1.8.1                 
#[151] backports_1.5.0             BiocParallel_1.40.0        
#[153] timechange_0.3.0            gtable_0.3.6               
#[155] rjson_0.2.23                ggridges_0.5.6             
#[157] progressr_0.15.1            parallel_4.4.0             
#[159] pROC_1.18.5                 ape_5.8-1                  
#[161] limma_3.62.2                jsonlite_1.8.9             
#[163] edgeR_4.4.2                 RcppHNSW_0.6.0             
#[165] bitops_1.0-9                Rtsne_0.17                 
#[167] spatstat.utils_3.1-3        BiocNeighbors_2.0.1        
#[169] RcppParallel_5.1.10         futile.options_1.0.1       
#[171] jquerylib_0.1.4             spatstat.univar_3.1-2      
#[173] timeDate_4041.110           lazyeval_0.2.2             
#[175] shiny_1.10.0                htmltools_0.5.8.1          
#[177] sctransform_0.4.1           formatR_1.14               
#[179] glue_1.8.0                  spam_2.11-1                
#[181] XVector_0.44.0              futile.logger_1.4.3        
#[183] gridExtra_2.3               R6_2.6.1                   
#[185] fdrtool_1.2.18              SingleCellExperiment_1.28.1
#[187] gplots_3.2.0                cluster_2.1.8.1            
#[189] rngtools_1.5.2              GenomeInfoDb_1.42.3        
#[191] ipred_0.9-15                statnet.common_4.11.0      
#[193] DelayedArray_0.32.0         tidyselect_1.2.1           
#[195] htmlTable_2.4.3             ggforce_0.4.2              
#[197] xml2_1.3.8                  car_3.1-3                  
#[199] ModelMetrics_1.2.2.2        munsell_0.5.1              
#[201] KernSmooth_2.23-26          data.table_1.17.0          
#[203] htmlwidgets_1.6.4           ComplexHeatmap_2.22.0      
#[205] RColorBrewer_1.1-3          rlang_1.1.5                
#[207] spatstat.sparse_3.1-0       spatstat.explore_3.4-2     
#[209] ggnewscale_0.5.1            parallelDist_0.2.6         
#[211] hardhat_1.4.1               prodlim_2024.06.25 

info <- sessionInfo()
```

paste("Analysis performed using R version", paste(info$R.version$major, info$R.version$minor, sep="."))
[1] "Analysis performed using R version 4.4.0"

```{r echo=FALSE}
pkg.info <- getPkgInfo(info)
kable(pkg.info, format = "html", row.names=F) %>% kable_styling()
```