---
title: "Fig6"
author: "Atsuki Taniguchi"
date: "`r format(Sys.time(), '%Y年%m月%d日')`"
output:
 html_document:
  toc: true
  toc_float: true
  toc_depth: 6 
  number_sections: true
---
```{=html}
<style>
div.blue pre { background-color:lightblue !important; }
div.blue pre.r { background-color:lightyellow !important; }
</style>
```
<div class = "blue">

```{r setup, include=FALSE}
library(kableExtra)

knitr::opts_chunk$set(cache=FALSE, echo=FALSE, comment="", warning=FALSE, message=FALSE, fig.width=10, fig.height=8)

```

```{r}
# Helper function for package info
getPkgInfo <- function(info){
  #info <- sessionInfo()
  pkg <- info$otherPkgs
  pkg.info <- t(sapply(pkg, function(p){
    out <- matrix(c(Package=ifelse(is.null(p$Package),"-",p$Package),
                    Version=ifelse(is.null(p$Version),"-",p$Version),
                    Title=ifelse(is.null(p$Title),"-",p$Title),
                    License=ifelse(is.null(p$License),"-",p$License),
                    Repository=ifelse(is.null(p$Repository),"-",p$Repository)), nrow=1, ncol=5)
  }))
  colnames(pkg.info) <- c("Package","Version","Overview","License","Repository")
  return(pkg.info)
}
```

# Loading packages
```{r}
library(Seurat);library(tidyverse);library(patchwork);library(clusterProfiler);library(msigdbr);library(AUCell);library(fields);library(pheatmap)
```

# load10X_spatial data
```{r}
# --- S2（EGFR_eligible）---
# Rep1
seu_S2_R1 <- Load10X_Spatial(
  data.dir = "~/Primarytumor/visium/SN123_A595688_Rep1",
  filename = "filtered_feature_bc_matrix.h5"
)

# Rep2
seu_S2_R2 <- Load10X_Spatial(
  data.dir = "~/Primarytumor/visium/SN124_A595688_Rep2",
  filename = "filtered_feature_bc_matrix.h5"
)

# --- S4（EGFR_ineligible）---
# Rep1
seu_S4_R1 <- Load10X_Spatial(
  data.dir = "~/Primarytumor/visium/SN84_A120838_Rep1",
  filename = "filtered_feature_bc_matrix.h5"
)

# Rep2
seu_S4_R2 <- Load10X_Spatial(
  data.dir = "~/Primarytumor/visium/SN84_A120838_Rep2",
  filename = "filtered_feature_bc_matrix.h5"
)

seu_S2_R1$sample <- "S2_Rep1"
seu_S2_R2$sample <- "S2_Rep2"
seu_S4_R1$sample <- "S4_Rep1"
seu_S4_R2$sample <- "S4_Rep2"

seu_S2_R1 <- NormalizeData(seu_S2_R1)
seu_S2_R2 <- NormalizeData(seu_S2_R2)
seu_S4_R1 <- NormalizeData(seu_S4_R1)
seu_S4_R2 <- NormalizeData(seu_S4_R2)
```

# Add Pathologist_Annotation to metadata from annotation file
```{r}
anno_base_path <- "~/Primarytumor/visium/Pathology_SpotAnnotations/"

sample_info <- list(
  list(object_name = "seu_S2_R1", file = "Pathologist_Annotations_SN123_A595688_Rep1.csv"),
  list(object_name = "seu_S2_R2", file = "Pathologist_Annotations_SN124_A595688_Rep2.csv"),
  list(object_name = "seu_S4_R1", file = "Pathologist_Annotations_SN84_A120838_Rep1.csv"),
  list(object_name = "seu_S4_R2", file = "Pathologist_Annotations_SN84_A120838_Rep2.csv")
)

# Merge annotation for each object
for (i in seq_along(sample_info)) {
  obj_name <- sample_info[[i]]$object_name
  file <- paste0(anno_base_path, sample_info[[i]]$file)

  anno <- read.csv(file)
  colnames(anno) <- c("barcode", "Pathologist_Annotation")

  obj <- get(obj_name)
  obj$Pathologist_Annotation <- anno$Pathologist_Annotation[match(Cells(obj), anno$barcode)]
  assign(obj_name, obj)
}
```

# Prepare data for CytoSPACE: Fig6B
```{r}
set.seed(123)

# expression matrixの作成
obj <- readRDS("~/Primarytumor/merge_rpca_LR.RDS")

CAF <- readRDS("~/Primarytumor/Fibroblast_addmarkers.RDS")
caf_cells <- colnames(CAF)
caf_types <- CAF$cell_type
names(caf_types) <- caf_cells
obj$cell_type[caf_cells] <- caf_types[caf_cells]

macrophage <- readRDS("~/Primarytumor/Mφ_addmarkers_SPP1.RDS")
macro_cells <- colnames(macrophage)
macro_types <- macrophage$M_type
names(macro_types) <- macro_cells
obj$cell_type[macro_cells] <- macro_types[macro_cells]

non_mycaf <- c("ADAMDEC1+Fib", "iCAF", "SOX6+Fib")
obj$cell_type <- ifelse(obj$cell_type %in% non_mycaf, "non-myCAF", obj$cell_type)

obj$cell_type[obj$cell_type %in% c("intermediate_Mφ", "CSF_Mφ")] <- "TAM"
obj$cell_type[obj$cell_type == "EGF_Mφ"] <- "TAMo"

included_types <- c(
  "non-myCAF", "myCAF", "Pericyte", 
  "B cell", "Plasma cell", 
  "Endothelial cell",
  "Epithelial cell", 
  "TAM", "TAMo", 
  "T cell"
)

obj <- subset(obj, subset = cell_type %in% included_types)
Idents(obj) <- "cell_type"
obj <- subset(obj,downsample=8000)
saveRDS(obj, "~/Primarytumor/merge_rpca_cytospace.RDS")

source("~/Primarytumor/visium/generate_cytospace_from_seurat_object.R")

generate_cytospace_from_scRNA_seurat_object(
  scrna_seurat = obj,
  dir_out = "~/Primarytumor/visium/cytospace/scRNA_geneexpression",
  fout_prefix = "",
  write_sparse = FALSE,
  rna_assay = "RNA"
)

#NOTE: Ensure the functions handle Seurat v5 correctly (e.g., GetAssayData, GetTissueCoordinates)

generate_cytospace_from_ST_seurat_object(
  st_seurat = seu_S2_R1,
  dir_out = "~/Primarytumor/visium/cytospace/S2_R1",
  fout_prefix = "",
  write_sparse = FALSE,
  slice = "slice1"
)

generate_cytospace_from_ST_seurat_object(
  st_seurat = seu_S2_R2,
  dir_out = "~/Primarytumor/visium/cytospace/S2_R2",
  fout_prefix = "",
  write_sparse = FALSE,
  slice = "slice1"
)

generate_cytospace_from_ST_seurat_object(
  st_seurat = seu_S4_R1,
  dir_out = "~/Primarytumor/visium/cytospace/S4_R1",
  fout_prefix = "",
  write_sparse = FALSE,
  slice = "slice1"
)

generate_cytospace_from_ST_seurat_object(
  st_seurat = seu_S4_R2,
  dir_out = "~/Primarytumor/visium/cytospace/S4_R2",
  fout_prefix = "",
  write_sparse = FALSE,
  slice = "slice1"
)

# stacked bar chart
df_S2_R1 <- read_csv("~/Primarytumor/visium/S2_R1_cytospace_results/cell_type_assignments_by_spot.csv")
df_S2_R2 <- read_csv("~/Primarytumor/visium/S2_R2_cytospace_results/cell_type_assignments_by_spot.csv")
df_S4_R1 <- read_csv("~/Primarytumor/visium/S4_R1_cytospace_results/cell_type_assignments_by_spot.csv")
df_S4_R2 <- read_csv("~/Primarytumor/visium/S4_R2_cytospace_results/cell_type_assignments_by_spot.csv")

process_data <- function(df, sample_name) {
  df %>%
    select(-`Total cells`, -`Epithelial cell`) %>%
    pivot_longer(-SpotID, names_to = "cell_type", values_to = "count") %>%
    group_by(cell_type) %>%
    summarise(total = sum(count), .groups = "drop") %>%
    mutate(percent = total / sum(total) * 100,
           sample = sample_name)
}

# 各データフレームに適用
data_S2_R1 <- process_data(df_S2_R1, "S2_R1")
data_S2_R2 <- process_data(df_S2_R2, "S2_R2")
data_S4_R1 <- process_data(df_S4_R1, "S4_R1")
data_S4_R2 <- process_data(df_S4_R2, "S4_R2")

plot_data <- bind_rows(data_S2_R1, data_S2_R2, data_S4_R1, data_S4_R2)

cell_type_levels <- c(
  "B cell", "Plasma cell","T cell",
  "TAM", "TAMo",
  "myCAF", "non-myCAF", "Pericyte", "Endothelial cell"
)

plot_data$cell_type <- factor(plot_data$cell_type, levels = cell_type_levels)

ggplot(plot_data, aes(x = sample, y = percent, fill = cell_type)) +
  geom_bar(stat = "identity") +
  
scale_fill_manual(values = c(
"myCAF"        = "#595959",  
"non-myCAF"            = "#7489a8",  
"Endothelial cell" = "#2e8b57",   
"Pericyte"         = "#4a7a94",  

"TAM"              = "#c0392b",   
"TAMo"             = "#af7ac5",  

"T cell"           = "#7d6599", 
"B cell"           = "#2e86c1",   
"Plasma cell"      = "#5dade2"    
))+
  theme(
  axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
  axis.text.y = element_text(size = 12),
  axis.title = element_blank(),
  legend.title = element_blank(),
  legend.text = element_text(size = 11),
  plot.title = element_text(size = 15, face = "bold")
) #Fig6B
```

# Add module scores and plot spatial features: Fig6A,suppleFig6A
```{r}
Epithelial_genes <- c("ELF3", "CLDN3", "LGALS4", "CLDN4", "KRT19", "EPCAM")
EREG <- c("EREG")
fibro_genes <- c("CALD1", "COL6A2", "COL1A2", "C1S", "COL3A1", "COL6A1")
myeloid_genes <- c("TYROBP", "FCER1G", "AIF1", "LYZ", "MS4A6A", "LST1")

#S2_R2
# Add scores
seu_S2_R1 <- AddModuleScore(seu_S2_R1, features = list(Epithelial_genes), name = "Epithelial Cell")
seu_S2_R1 <- AddModuleScore(seu_S2_R1, features = list(fibro_genes), name = "Fibroblast")
seu_S2_R1 <- AddModuleScore(seu_S2_R1, features = list(myeloid_genes), name = "Myeloid cell")

#S4_R1
# Add scores
seu_S4_R2 <- AddModuleScore(seu_S4_R2, features = list(Epithelial_genes), name = "Epithelial Cell")
seu_S4_R2 <- AddModuleScore(seu_S4_R2, features = list(fibro_genes), name = "Fibroblast")
seu_S4_R2 <- AddModuleScore(seu_S4_R2, features = list(myeloid_genes), name = "Myeloid cell")

seu_S2_R1@images[["slice1"]]@scale.factors$spot <- seu_S2_R1@images[["slice1"]]@scale.factors$spot * 2.3
seu_S2_R2@images[["slice1"]]@scale.factors$spot <- seu_S2_R2@images[["slice1"]]@scale.factors$spot * 2.3
seu_S4_R1@images[["slice1"]]@scale.factors$spot <- seu_S4_R1@images[["slice1"]]@scale.factors$spot * 2.3
seu_S4_R2@images[["slice1"]]@scale.factors$spot <- seu_S4_R2@images[["slice1"]]@scale.factors$spot * 2.3


palette_1 <- colorRampPalette(c("navy", "blue", "lightgreen", "yellow"))(100)
palette_2 <- colorRampPalette(c("navy", "lightgreen", "yellow"))(100)

p1 <- SpatialFeaturePlot(seu_S2_R1, features = "Epithelial Cell1") +
  scale_fill_gradientn(colours = palette_1)
p2 <- SpatialFeaturePlot(seu_S2_R1, features = "Fibroblast1") +
  scale_fill_gradientn(colours = palette_1)
p3 <- SpatialFeaturePlot(seu_S2_R1, features = "Myeloid cell1") +
  scale_fill_gradientn(colours = palette_1)
p <- p1 + p2 + p3 + plot_layout(ncol = 3) #SFig6A-1

p4 <- SpatialFeaturePlot(seu_S4_R2, features = "Epithelial Cell1")+
  scale_fill_gradientn(colours = palette_1)
p5 <- SpatialFeaturePlot(seu_S4_R2, features = "Fibroblast1")+
  scale_fill_gradientn(colours = palette_1)
p6 <- SpatialFeaturePlot(seu_S4_R2, features = "Myeloid cell1")+
  scale_fill_gradientn(colours = palette_1)
p <- p4 + p5 + p6 + plot_layout(ncol = 3) #SFig6A-2

p7 <- SpatialFeaturePlot(seu_S2_R1, features = "EREG")+
  scale_fill_gradientn(
    colours = palette_2,
    limits = c(0,3))
p8 <- SpatialFeaturePlot(seu_S4_R2, features = "EREG")+
  scale_fill_gradientn(
    colours = palette_2,
    limits = c(0,3))
p <- p7 + p8 + plot_layout(ncol = 2) #Fig6A-3

SpatialDimPlot(seu_S2_R1, group.by = "Pathologist_Annotation", label = TRUE, repel = TRUE)
SpatialDimPlot(seu_S2_R2, group.by = "Pathologist_Annotation", label = TRUE, repel = TRUE)
SpatialDimPlot(seu_S4_R1, group.by = "Pathologist_Annotation", label = TRUE, repel = TRUE)
SpatialDimPlot(seu_S4_R2, group.by = "Pathologist_Annotation", label = TRUE, repel = TRUE)
```

# Tumor Proximity Analysis: Fig6C
```{r}
# Hallmark pathways
hallmark_paths <- c(
  "HALLMARK_PI3K_AKT_MTOR_SIGNALING",
  "HALLMARK_TNFA_SIGNALING_VIA_NFKB",
  "HALLMARK_TGF_BETA_SIGNALING",
  "HALLMARK_IL6_JAK_STAT3_SIGNALING",
  "HALLMARK_INFLAMMATORY_RESPONSE",
  "HALLMARK_HYPOXIA",
  "HALLMARK_INTERFERON_GAMMA_RESPONSE",
  "HALLMARK_APOPTOSIS",
  "HALLMARK_WNT_BETA_CATENIN_SIGNALING",
  "HALLMARK_ANGIOGENESIS"
)

# Non-Hallmark pathways (e.g., C2, C5, C7)
non_hallmark_paths <- c(
  "REACTOME_SIGNALING_BY_EGFR",
  "KEGG_ERBB_SIGNALING_PATHWAY",
  "REACTOME_EXTRACELLULAR_MATRIX_ORGANIZATION",
  "REACTOME_INTERLEUKIN_10_SIGNALING",
  "REACTOME_CYTOKINE_SIGNALING_IN_IMMUNE_SYSTEM",
  "KEGG_PATHWAYS_IN_CANCER"
)

all_pathways <- c(hallmark_paths, non_hallmark_paths)
all_sets <- msigdbr(species = "Homo sapiens")
selected_sets <- all_sets %>%
  filter(gs_name %in% all_pathways)
pathway_genesets <- split(selected_sets$gene_symbol, selected_sets$gs_name)

run_aucell <- function(seu_obj) {
  expr_matrix <- GetAssayData(seu_obj, slot = "data")
  expr_mat <- as.matrix(expr_matrix)
  rankings <- AUCell_buildRankings(expr_mat, nCores = 1, plotStats = FALSE)
  auc <- AUCell_calcAUC(pathway_genesets, rankings, nCores = 1)
  auc_df <- as.data.frame(t(getAUC(auc)))
  seu_obj <- AddMetaData(seu_obj, metadata = auc_df)
  return(seu_obj)
}

# Run AUCell
seu_S2_R1 <- run_aucell(seu_S2_R1)
seu_S2_R2 <- run_aucell(seu_S2_R2)
seu_S4_R1 <- run_aucell(seu_S4_R1)
seu_S4_R2 <- run_aucell(seu_S4_R2)

samples <- list(
  S2_Rep1 = seu_S2_R1,
  S4_Rep2 = seu_S4_R2
)

for (sample_name in names(samples)) {
  seu <- samples[[sample_name]]
  
  for (pw in pathways_of_interest) {
    print(SpatialFeaturePlot(seu, features = pw, alpha = c(0.3, 1)) +
            ggtitle(paste0(sample_name, " - ", pw)))
  }
}

#S2_R1
coords <- GetTissueCoordinates(seu_S2_R1)
anno <- seu_S2_R1@meta.data$Pathologist_Annotation
names(anno) <- rownames(seu_S2_R1@meta.data)

stroma_spots <- names(anno)[anno %in% c("stroma_fibroblastic_IC high", "stroma_fibroblastic_IC med", "stroma_fibroblastic_IC_high", "stroma_fibroblastic_IC_med", "stroma_fibroblastic_IC low")]
tumor_spots <- names(anno)[anno %in% c("tumor", "tumor&stroma_IC med to high","tumor&stroma_IC low")]

dist_matrix <- rdist(
  as.matrix(coords[stroma_spots, c("x", "y")]),
  as.matrix(coords[tumor_spots, c("x", "y")])
)
min_distances <- apply(dist_matrix, 1, min)

threshold <- median(min_distances)
threshold

stroma_group <- ifelse(min_distances <= threshold, "Near", "Far")

seu_S2_R1$TumorProximityGroup <- NA
seu_S2_R1$TumorProximityGroup[stroma_spots] <- stroma_group


# S2_R2
coords <- GetTissueCoordinates(seu_S2_R2)
anno <- seu_S2_R2@meta.data$Pathologist_Annotation
names(anno) <- rownames(seu_S2_R2@meta.data)

stroma_spots <- names(anno)[anno %in% c("stroma_fibroblastic_IC high", "stroma_fibroblastic_IC med", "stroma_fibroblastic_IC_high", "stroma_fibroblastic_IC_med", "stroma_fibroblastic_IC low")]
tumor_spots <- names(anno)[anno %in% c("tumor", "tumor&stroma_IC med to high","tumor&stroma_IC low")]

dist_matrix <- rdist(
  as.matrix(coords[stroma_spots, c("x", "y")]),
  as.matrix(coords[tumor_spots, c("x", "y")])
)
min_distances <- apply(dist_matrix, 1, min)

threshold <- median(min_distances)
threshold

stroma_group <- ifelse(min_distances <= threshold, "Near", "Far")

seu_S2_R2$TumorProximityGroup <- NA
seu_S2_R2$TumorProximityGroup[stroma_spots] <- stroma_group

# S4_R1
coords <- GetTissueCoordinates(seu_S4_R1)
anno <- seu_S4_R1@meta.data$Pathologist_Annotation
names(anno) <- rownames(seu_S4_R1@meta.data)

stroma_spots <- names(anno)[anno %in% c("stroma_fibroblastic_IC high", "stroma_fibroblastic_IC med", "stroma_fibroblastic_IC_high", "stroma_fibroblastic_IC_med", "stroma_fibroblastic_IC low")]
tumor_spots <- names(anno)[anno %in% c("tumor", "tumor&stroma_IC med to high","tumor&stroma_IC low")]

dist_matrix <- rdist(
  as.matrix(coords[stroma_spots, c("x", "y")]),
  as.matrix(coords[tumor_spots, c("x", "y")])
)
min_distances <- apply(dist_matrix, 1, min)

threshold <- median(min_distances)
threshold

stroma_group <- ifelse(min_distances <= threshold, "Near", "Far")

seu_S4_R1$TumorProximityGroup <- NA
seu_S4_R1$TumorProximityGroup[stroma_spots] <- stroma_group

# S4_R2
coords <- GetTissueCoordinates(seu_S4_R2)
anno <- seu_S4_R2@meta.data$Pathologist_Annotation
names(anno) <- rownames(seu_S4_R2@meta.data)

stroma_spots <- names(anno)[anno %in% c("stroma_fibroblastic_IC high", "stroma_fibroblastic_IC med", "stroma_fibroblastic_IC_high", "stroma_fibroblastic_IC_med", "stroma_fibroblastic_IC low")]
tumor_spots <- names(anno)[anno %in% c("tumor", "tumor&stroma_IC med to high","tumor&stroma_IC low")]

dist_matrix <- rdist(
  as.matrix(coords[stroma_spots, c("x", "y")]),
  as.matrix(coords[tumor_spots, c("x", "y")])
)
min_distances <- apply(dist_matrix, 1, min)

threshold <- median(min_distances)
threshold

stroma_group <- ifelse(min_distances <= threshold, "Near", "Far")

seu_S4_R2$TumorProximityGroup <- NA
seu_S4_R2$TumorProximityGroup[stroma_spots] <- stroma_group

SpatialDimPlot(seu_S2_R1, group.by = "TumorProximityGroup", label = F )+
  theme(
    legend.position = "bottom"
  ) #Fig6C-2

SpatialDimPlot(seu_S2_R2, group.by = "TumorProximityGroup", label = F )
SpatialDimPlot(seu_S4_R1, group.by = "TumorProximityGroup", label = F )

SpatialDimPlot(seu_S4_R2, group.by = "TumorProximityGroup", label = F )+
  theme(
    legend.position = "bottom"
  ) #Fig6C-1


# Heatmap of pathway scores by proximity group
# Store all relevant Seurat objects in a list
samples <- list(
  S2_Rep1 = seu_S2_R1,
  S2_Rep2 = seu_S2_R2,
  S4_Rep1 = seu_S4_R1,
  S4_Rep2 = seu_S4_R2
)

# Create matrix: pathway scores by proximity group and sample
summary_list <- list()

for (sample_name in names(samples)) {
  obj <- samples[[sample_name]]
  
  for (grp in c("Near", "Far")) {
    spot_subset <- obj@meta.data %>%
      filter(TumorProximityGroup == grp)
    mean_scores <- colMeans(spot_subset[, all_pathways], na.rm = TRUE)
    rowname <- paste(grp, sample_name, sep = "_")
    summary_list[[rowname]] <- mean_scores
  }
}

heatmap_df <- do.call(rbind, summary_list)
heatmap_matrix <- t(heatmap_df)

order_cols <- c(
  "Near_S2_Rep1",
  "Far_S2_Rep1",
  "Near_S4_Rep2",
  "Far_S4_Rep2"
)

order_rows <- c(
  "REACTOME_SIGNALING_BY_EGFR",
  "KEGG_ERBB_SIGNALING_PATHWAY",
  "HALLMARK_PI3K_AKT_MTOR_SIGNALING",
  "HALLMARK_IL6_JAK_STAT3_SIGNALING",
  "REACTOME_INTERLEUKIN_10_SIGNALING",
  "KEGG_PATHWAYS_IN_CANCER",
  "REACTOME_EXTRACELLULAR_MATRIX_ORGANIZATION",
  "HALLMARK_TNFA_SIGNALING_VIA_NFKB",
  "HALLMARK_TGF_BETA_SIGNALING",
  "HALLMARK_HYPOXIA",
  "HALLMARK_INTERFERON_GAMMA_RESPONSE",
  "HALLMARK_APOPTOSIS",
  "HALLMARK_ANGIOGENESIS"
)

heatmap_matrix <- heatmap_matrix[order_rows, order_cols]

pheatmap(
  mat = heatmap_matrix,
  scale = "row",
  cluster_rows = FALSE,
  cluster_cols = FALSE, 
  color = colorRampPalette(c("navy", "white", "firebrick3"))(100),
  gaps_col = 2
) #Fig6C-3
```

# Identify and characterize spots with co-occurring non-myCAF and TAM/TAMo signatures: suppleFig6B-1,2
```{r}
Epithelial_genes <- list(c("ELF3", "CLDN3", "LGALS4", "CLDN4", "KRT19", "EPCAM"))
Fibro_genes <- list("COL1A2")
TAM_genes <- list(c("SPP1", "CSF1R")) 
TAMo_genes <- list(c("EREG","CD14", "S100A8"))  
IC_genes <- list(c("CD3D", "PTPRC"))
Endothelial_genes <- list(c("VIM", "VWF"))

seu_S4_R2 <- AddModuleScore(seu_S4_R2, features = Epithelial_genes, name = "Epithelial")
seu_S4_R2 <- AddModuleScore(seu_S4_R2, features = Fibro_genes, name = "Fibro")
seu_S4_R2 <- AddModuleScore(seu_S4_R2, features = TAM_genes, name = "TAM")
seu_S4_R2 <- AddModuleScore(seu_S4_R2, features = TAMo_genes, name = "TAMo")
seu_S4_R2 <- AddModuleScore(seu_S4_R2, features = IC_genes, name = "IC")
seu_S4_R2 <- AddModuleScore(seu_S4_R2, features = Endothelial_genes, name = "Endothelial")

seu_S2_R1 <- AddModuleScore(seu_S2_R1, features = Epithelial_genes, name = "Epithelial")
seu_S2_R1 <- AddModuleScore(seu_S2_R1, features = Fibro_genes, name = "Fibro")
seu_S2_R1 <- AddModuleScore(seu_S2_R1, features = TAM_genes, name = "TAM")
seu_S2_R1 <- AddModuleScore(seu_S2_R1, features = TAMo_genes, name = "TAMo")
seu_S2_R1 <- AddModuleScore(seu_S2_R1, features = IC_genes, name = "IC")
seu_S2_R1 <- AddModuleScore(seu_S2_R1, features = Endothelial_genes, name = "Endothelial")

seu_S4_R2$FAP_expr <- FetchData(seu_S4_R2, vars = "FAP")[,1]
seu_S2_R1$FAP_expr <- FetchData(seu_S2_R1, vars = "FAP")[,1]

seu_S4_R2$Fig6D_Group <- NA
seu_S4_R2$Fig6D_Group[seu_S4_R2$IC1 > 0.05 & seu_S4_R2$Fibro1 < 0.5 ] <- "immune cell"
seu_S4_R2$Fig6D_Group[seu_S4_R2$Fibro1 > 0.5 & seu_S4_R2$FAP_expr < 0.5] <- "non-myCAF"
seu_S4_R2$Fig6D_Group[seu_S4_R2$FAP_expr > 0.5] <- "myCAF"
seu_S4_R2$Fig6D_Group[seu_S4_R2$Fibro1 > 0.5 & seu_S4_R2$FAP_expr > 0.5 & seu_S4_R2$TAM1 > 0.5] <- "myCAF + TAM"
seu_S4_R2$Fig6D_Group[seu_S4_R2$Fibro1 > 0.5 & seu_S4_R2$FAP_expr > 0.5 & seu_S4_R2$TAMo1 > 0.5] <- "myCAF + TAMo"
seu_S4_R2$Fig6D_Group[seu_S4_R2$Fibro1 > 0.5 & seu_S4_R2$FAP_expr < 0.5 & seu_S4_R2$TAM1 > 0.5] <- "non-myCAF + TAM"
seu_S4_R2$Fig6D_Group[seu_S4_R2$Fibro1 > 0.5 & seu_S4_R2$FAP_expr < 0.5 & seu_S4_R2$TAMo1 > 0.5] <- "non-myCAF + TAMo"
seu_S4_R2$Fig6D_Group[seu_S4_R2$Epithelial1 > 0.8] <- "Epithelial cell"
seu_S4_R2$Fig6D_Group[is.na(seu_S4_R2$Fig6D_Group)] <- "Unknown"

seu_S2_R1$Fig6D_Group <- NA
seu_S2_R1$Fig6D_Group[seu_S2_R1$IC1 > 0.05 & seu_S2_R1$Fibro1 < 0.5 ] <- "immune cell"
seu_S2_R1$Fig6D_Group[seu_S2_R1$Fibro1 > 0.5 & seu_S2_R1$FAP_expr < 0.5] <- "non-myCAF"
seu_S2_R1$Fig6D_Group[seu_S2_R1$FAP_expr > 0.5] <- "myCAF"
seu_S2_R1$Fig6D_Group[seu_S2_R1$Fibro1 > 0.5 & seu_S2_R1$FAP_expr > 0.5 & seu_S2_R1$TAM1 > 0.5] <- "myCAF + TAM"
seu_S2_R1$Fig6D_Group[seu_S2_R1$Fibro1 > 0.5 & seu_S2_R1$FAP_expr > 0.5 & seu_S2_R1$TAMo1 > 0.5] <- "myCAF + TAMo"
seu_S2_R1$Fig6D_Group[seu_S2_R1$Fibro1 > 0.5 & seu_S2_R1$FAP_expr < 0.5 & seu_S2_R1$TAM1 > 0.4] <- "non-myCAF + TAM" #TAM1：0.5→0.4
seu_S2_R1$Fig6D_Group[seu_S2_R1$Fibro1 > 0.5 & seu_S2_R1$FAP_expr < 0.5 & seu_S2_R1$TAMo1 > 0.3] <- "non-myCAF + TAMo" #TAMo1：0.5→0.3
seu_S2_R1$Fig6D_Group[seu_S2_R1$Epithelial1 > 0.9] <- "Epithelial cell" #Epithelial：0.8→0.9
seu_S2_R1$Fig6D_Group[is.na(seu_S2_R1$Fig6D_Group)] <- "Unknown"


seu_S4_R2@meta.data[["Fig6D_Group"]] %>% table()
seu_S2_R1@meta.data[["Fig6D_Group"]] %>% table()

group_colors <- c(
  "non-myCAF + TAMo"      = "#87CEEB",   # light blue
  "non-myCAF + TAM"       = "#228B22",   # forestgreen
  "non-myCAF"             = "#CD6600",   # dark orange
  "myCAF + TAMo"                  = "#4682B4",   # steelblue
  "myCAF + TAM"                   = "#006400",   # darkgreen
  "myCAF"                 = "#8B008B",   # darkmagenta
  "Epithelial cell"       = "navy",      # epithelial
  "immune cell"           = "#DB7093",   # pinkish
  "Unknown"               = "#D3D3D3"    # gray
)

SpatialDimPlot(seu_S4_R2, group.by = "Fig6D_Group",cols = group_colors)+
  theme(
    legend.position = "bottom"
  )
SpatialDimPlot(seu_S2_R1, group.by = "Fig6D_Group", cols = group_colors) +
  theme(legend.position = "bottom")

genes_to_check <- c(
  "COL1A2", "FAP",   
  "SPP1", "CSF1R",
  "ELF3",
  "EREG", "AREG", "CD14","S100A8",
  "VIM", "VWF",
  "PTPRC", "CD3D"
)

group_order <- c(
  "Unknown",
  "immune cell",
  "Epithelial cell",
  "non-myCAF + TAMo",
  "non-myCAF + TAM",
  "myCAF + TAMo",
  "myCAF + TAM",
  "non-myCAF",
  "myCAF"
)

Idents(seu_S4_R2) <- factor(seu_S4_R2$Fig6D_Group, levels = group_order)
Idents(seu_S2_R1) <- factor(seu_S2_R1$Fig6D_Group, levels = group_order)

DotPlot(seu_S4_R2, features = genes_to_check) +
  RotatedAxis() +
  scale_color_gradientn(colors = c("navy", "white", "firebrick3"))
DotPlot(seu_S2_R1, features = genes_to_check) +
  RotatedAxis() +
  scale_color_gradientn(colors = c("navy", "white", "firebrick3"))

# Use Reactome and Hallmark gene sets (optionally: all C2, etc.)
msig <- msigdbr(species = "Homo sapiens", category = "C2", subcategory = "REACTOME")
hallmark <- msigdbr(species = "Homo sapiens", category = "H")

msig_all <- rbind(msig, hallmark)

unique(msig_all$gs_name[grepl("EGFR|EREG|ERBB|PROLIFERATION", msig_all$gs_name, ignore.case = TRUE)])

egfr_pathways <- c(
  "REACTOME_SIGNALING_BY_EGFR",
  "REACTOME_SIGNALING_BY_ERBB2",
  "REACTOME_PI3K_EVENTS_IN_ERBB2_SIGNALING",
  "REACTOME_POU5F1_OCT4_SOX2_NANOG_ACTIVATE_GENES_RELATED_TO_PROLIFERATION"
)

egfr_term2gene <- msig_all %>%
  filter(gs_name %in% egfr_pathways) %>%
  dplyr::select(gs_name, gene_symbol)  

#GSEA
deg <- FindMarkers(
  seu_S4_R2,
  ident.1 = "non-myCAF",
  ident.2 = "myCAF",
  slot = "data",
  logfc.threshold = 0,
  min.pct = 0
)

gene_list <- deg$avg_log2FC
names(gene_list) <- rownames(deg)
gene_list <- sort(gene_list, decreasing = TRUE)

gsea <- GSEA(
  geneList = gene_list,
  TERM2GENE = egfr_term2gene, 
  pvalueCutoff = 0.1
)

for (gs_id in gsea@result[["ID"]]) {
  p <- gseaplot2(
    gsea, 
    geneSetID = gs_id,
    title = gs_id, 
    base_size = 7 
  )
  } #suppleFig6B-1,2
```

# Session Information
```{r echo=FALSE}
sessionInfo()
#R version 4.4.0 (2024-04-24 ucrt)
#Platform: x86_64-w64-mingw32/x64
#Running under: Windows 11 x64 (build 26100)

#Matrix products: default


#locale:
#[1] LC_COLLATE=Japanese_Japan.utf8  LC_CTYPE=Japanese_Japan.utf8   
#[3] LC_MONETARY=Japanese_Japan.utf8 LC_NUMERIC=C                   
#[5] LC_TIME=Japanese_Japan.utf8    

#time zone: Asia/Tokyo
#tzcode source: internal

#attached base packages:
#[1] stats     graphics  grDevices utils     datasets  methods  
#[7] base     

#other attached packages:
# [1] pheatmap_1.0.12        fields_16.3.1         
# [3] viridisLite_0.4.2      spam_2.11-1           
# [5] AUCell_1.28.0          msigdbr_10.0.1        
# [7] clusterProfiler_4.14.4 patchwork_1.3.0       
# [9] lubridate_1.9.4        forcats_1.0.0         
#[11] stringr_1.5.1          dplyr_1.1.4           
#[13] purrr_1.0.4            readr_2.1.5           
#[15] tidyr_1.3.1            tibble_3.2.1          
#[17] ggplot2_3.5.1          tidyverse_2.0.0       
#[19] Seurat_5.2.1           SeuratObject_5.0.2    
#[21] sp_2.2-0               kableExtra_1.4.0      

#loaded via a namespace (and not attached):
#  [1] RcppAnnoy_0.0.22            splines_4.4.0              
#  [3] later_1.4.2                 ggplotify_0.1.2            
#  [5] R.oo_1.27.0                 polyclip_1.10-7            
#  [7] graph_1.84.1                XML_3.99-0.18              
#  [9] fastDummies_1.7.5           lifecycle_1.0.4            
# [11] globals_0.16.3              lattice_0.22-6             
# [13] MASS_7.3-65                 magrittr_2.0.3             
# [15] plotly_4.10.4               rmarkdown_2.29             
# [17] yaml_2.3.10                 ggtangle_0.0.6             
# [19] httpuv_1.6.15               sctransform_0.4.1          
# [21] spatstat.sparse_3.1-0       reticulate_1.42.0          
# [23] cowplot_1.1.3               pbapply_1.7-2              
# [25] DBI_1.2.3                   RColorBrewer_1.1-3         
# [27] maps_3.4.2.1                abind_1.4-8                
# [29] zlibbioc_1.50.0             GenomicRanges_1.56.1       
# [31] Rtsne_0.17                  R.utils_2.13.0             
# [33] BiocGenerics_0.52.0         yulab.utils_0.2.0          
# [35] GenomeInfoDbData_1.2.13     enrichplot_1.26.6          
# [37] IRanges_2.38.1              S4Vectors_0.42.1           
# [39] ggrepel_0.9.6               irlba_2.3.5.1              
# [41] listenv_0.9.1               spatstat.utils_3.1-3       
# [43] tidytree_0.4.6              goftest_1.2-3              
# [45] RSpectra_0.16-2             annotate_1.84.0            
# [47] spatstat.random_3.3-3       fitdistrplus_1.2-2         
# [49] parallelly_1.43.0           DelayedMatrixStats_1.28.1  
# [51] svglite_2.1.3               DelayedArray_0.32.0        
# [53] codetools_0.2-20            DOSE_4.0.0                 
# [55] xml2_1.3.8                  tidyselect_1.2.1           
# [57] aplot_0.2.5                 UCSC.utils_1.2.0           
# [59] farver_2.1.2                matrixStats_1.5.0          
# [61] stats4_4.4.0                spatstat.explore_3.4-2     
# [63] jsonlite_1.8.9              progressr_0.15.1           
# [65] ggridges_0.5.6              survival_3.8-3             
# [67] systemfonts_1.2.2           tools_4.4.0                
# [69] treeio_1.30.0               ica_1.0-3                  
# [71] Rcpp_1.0.14                 glue_1.8.0                 
# [73] SparseArray_1.6.1           gridExtra_2.3              
# [75] xfun_0.52                   MatrixGenerics_1.18.1      
# [77] qvalue_2.38.0               GenomeInfoDb_1.42.3        
# [79] withr_3.0.2                 fastmap_1.2.0              
# [81] digest_0.6.37               gridGraphics_0.5-1         
# [83] timechange_0.3.0            R6_2.6.1                   
# [85] mime_0.13                   colorspace_2.1-1           
# [87] scattermore_1.2             GO.db_3.20.0               
# [89] tensor_1.5                  spatstat.data_3.1-6        
# [91] RSQLite_2.3.9               R.methodsS3_1.8.2          
# [93] generics_0.1.3              data.table_1.17.0          
# [95] S4Arrays_1.4.1              httr_1.4.7                 
# [97] htmlwidgets_1.6.4           uwot_0.2.3                 
# [99] pkgconfig_2.0.3             gtable_0.3.6               
#[101] blob_1.2.4                  lmtest_0.9-40              
#[103] XVector_0.44.0              htmltools_0.5.8.1          
#[105] dotCall64_1.2               fgsea_1.33.1               
#[107] msigdbdf_24.1.0             GSEABase_1.68.0            
#[109] scales_1.3.0                Biobase_2.64.0             
#[111] png_0.1-8                   spatstat.univar_3.1-2      
#[113] ggfun_0.1.8                 knitr_1.50                 
#[115] rstudioapi_0.17.1           tzdb_0.5.0                 
#[117] reshape2_1.4.4              nlme_3.1-168               
#[119] zoo_1.8-13                  cachem_1.1.0               
#[121] KernSmooth_2.23-26          parallel_4.4.0             
#[123] miniUI_0.1.1.1              AnnotationDbi_1.68.0       
#[125] pillar_1.10.2               grid_4.4.0                 
#[127] vctrs_0.6.5                 RANN_2.6.2                 
#[129] promises_1.3.2              xtable_1.8-4               
#[131] cluster_2.1.8.1             evaluate_1.0.3             
#[133] cli_3.6.3                   compiler_4.4.0             
#[135] rlang_1.1.5                 crayon_1.5.3               
#[137] future.apply_1.11.3         plyr_1.8.9                 
#[139] fs_1.6.5                    stringi_1.8.7              
#[141] deldir_2.0-4                BiocParallel_1.40.0        
#[143] babelgene_22.9              assertthat_0.2.1           
#[145] munsell_0.5.1               Biostrings_2.74.1          
#[147] lazyeval_0.2.2              spatstat.geom_3.3-6        
#[149] GOSemSim_2.32.0             Matrix_1.7-2               
#[151] RcppHNSW_0.6.0              hms_1.1.3                  
#[153] sparseMatrixStats_1.18.0    bit64_4.6.0-1              
#[155] future_1.34.0               KEGGREST_1.46.0            
#[157] shiny_1.10.0                SummarizedExperiment_1.36.0
#[159] ROCR_1.0-11                 igraph_2.1.4               
#[161] memoise_2.0.1               ggtree_3.14.0              
#[163] fastmatch_1.1-6             bit_4.6.0                  
#[165] gson_0.1.0                  ape_5.8-1 

info <- sessionInfo()
```

paste("Analysis performed using R version", paste(info$R.version$major, info$R.version$minor, sep="."))
[1] "Analysis performed using R version 4.4.0"

```{r echo=FALSE}
pkg.info <- getPkgInfo(info)
kable(pkg.info, format = "html", row.names=F) %>% kable_styling()
```
